### 2019-03-04 README.Rmd
added badges and bumped R version

**Background**

@@

**Methods**

@@

**Results:**

@@

**Conclusions**

@@

# Docker

>>>>

[![Documentation](https://img.shields.io/badge/Documentation-click here!-lightgrey.svg?style=flat)](https://www.samabbott.co.uk/DirectEffBCGPolicyChange)
[![badge](https://img.shields.io/badge/Launch-Analysis-lightblue.svg)](https://mybinder.org/v2/gh/seabbs/DirectEffBCGPolicyChange/master?urlpath=rstudio)
[![DOI](https://zenodo.org/badge/173767331.svg)](https://zenodo.org/badge/latestdoi/173767331)

## Abstract

### Background

@@

### Methods

@@

### Results

@@

### Conclusions

@@

## Reproducibility

## Docker
